Frozen Civil Conflicts

### 2024-02-12 paper.qmd
Follow bayesplot and use 90% CIs

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction")) +
    facet_grid(. ~ group) +
    scale_fill_solarized()
```

@@

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip() +
    facet_grid(. ~ group) +
    scale_fill_solarized()
```

>>>>

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8, show.legend = F, .width = c(0.5, 0.9)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction")) +
    facet_grid(. ~ group) +
    scale_fill_solarized()
```

@@

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F, .width = c(0.5, 0.9)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip() +
    facet_grid(. ~ group) +
    scale_fill_solarized()
```
